### 2018-01-29 polarization/paper.tex
Two polarizer analysis

	In this experiment, ...

@@

	Analysis goes here

>>>>

	In this experiment, \textbf{TODO}.

@@

	To begin with, Malus's law was verified using the obtained data for two polarizers. Fitting the measured intensity and angles to \( \cos \theta \) using the least squares method yielded a poor fit characterized by a reduced \( \chi ^ 2 \) of \( 48020.4 \) and an \( R^2 \) value of \( -1.53364 \). Fitting the data to \eqMalusLaw instead (i.e. testing a dependence on cosine squared) yielded a better fit characterized by a reduced \( \chi ^ 2 \)	of \( 8.56036 \) and an \( R ^ 2 \) value of \( 0.999548 \), indicating that the data obeys the theoretical model. The fit parameter was determined to be \( I_0 = 3.8269 \pm 0.0008 \). A visualization of the fit along with residuals is shown below.
	\paperfig{Exercise1Fit}{\pdf{exercise1-model}}{Light intensity and and fit residuals plotted against the angular position of the sensor for the two polarizer setup. The curve in red has the function \( 3.8269 \pm 0.0008 \cos ^ 2 \theta \). Error bars were included but are too small to be visible.}
